% LaTeX Curriculum Vitae Template

\documentclass{article}
%\documentclass[10pt]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{color}


% Set your name here
\def\name{Kai Yang}
\definecolor{mygrey}{gray}{0.85}
\definecolor{homepagecolor}{RGB}{20,43,140}
\newcommand{\homepage}[3][homepagecolor]{\href{#2}{\color{#1}{#3}}}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  % right=0.8in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
%\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\large}
%\subsectionfont{\rmfamily\mdseries\itshape\normalsize}
\subsectionfont{\normalsize\it\bfseries}


% Don't indent paragraphs.
\setlength\parindent{0em}


\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.2in}

\begin{minipage}{0.55\linewidth}
  \href{http://www.shanghaitech.edu.cn}{ShanghaiTech University} \\
  School of Information Science and Technology \\
393 Middle Huaxia Road, Pudong, Shanghai 201210, China
\end{minipage}\hspace{2em}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (86) 153-0379-6255 \\
    Email: & \href{mailto:yangkai@shanghaitech.edu.cn}{\tt yangkai@shanghaitech.edu.cn} \\ &\\
  \end{tabular}
\end{minipage}


\section*{\colorbox{mygrey}{Education~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}}
{\bf{ShanghaiTech University}}, Shanghai, China

Ph.D. candidate in Communication and Information Systems, 09/2015-07/2020 (expected) 
\begin{itemize}
  \item Advisor: \homepage{http://shiyuanming.github.io/}{Prof. Yuanming Shi}
  \item School of Information Science and Technology
  \item Research Topic: {{Generalized Sparse and Low-Rank Optimization for Dense Wireless Networks}}
\end{itemize}

{\bf{Dalian University of Technology}}, Dalian, China

B.E. in Electronic Engineering, 09/2011--07/2015
\begin{itemize}
\item Advisor: \homepage{http://faculty.dlut.edu.cn/GuoYanqing}{Prof. Yanqing Guo}
\item School of Information and Communication Engineering 09/2013--07/2015
\item Faculty of Electronic Information and Electrical Engineering 09/2011--07/2013
\end{itemize}





\section*{\colorbox{mygrey}{Honors and Awards~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}}
\begin{itemize}
\item National Scholarship for Graduate Students, 2017
\item Student Merit Award, University of Chinese Academy of Science, 2017
\item Student Merit Award, ShanghaiTech University, 2016
\end{itemize}

\section*{\colorbox{mygrey}{Experience~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}}
{\bf{University of Toronto}}, Ontario, Canada

Visiting student, 2019.01-2020.01
\begin{itemize}
\item Host: \homepage{https://www.comm.utoronto.ca/~weiyu/}{Prof. Wei Yu}
\end{itemize}


{\bf{University of California, Berkeley}}, California, USA

Visiting student in BeSTEC program, 2016.10-2017.02
\begin{itemize}
\item Host: \homepage{https://people.eecs.berkeley.edu/~wainwrig/}{Prof. Martin J. Wainwright}
\end{itemize}


\section*{\colorbox{mygrey}{Research Interests~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}}
My research interests include sparse and low-rank optimization, manifold optimization, machine learning, and their applications to dense wireless networks and distributed computing systems:
\begin{itemize}
   \item convex and nonconvex optimization
   \item mobile edge artificial intelligence
   \item edge computing and caching
   \item intelligent IoT
 \end{itemize} 
\section*{\colorbox{mygrey}{Publications~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}}

\subsection*{Book Chapters}
\begin{enumerate}
\item Y. Shi, {\bf{K. Yang}}, and Y. Yang,
``Generalized Low-Rank Optimization for Ultra-Dense Fog-RANs," in {\emph{Ultra Dense Networks: Principles and Technologies}}, Cambridge University Press, 2019.
\end{enumerate}

\subsection*{Journal Articles}

\begin{enumerate}
\item {\bf{K. Yang}}, T. Jiang, Y. Shi, and Z. Ding, “Federated learning via over-the-air computation,” submitted.
\item {\bf{K. Yang}}, Y. Shi, and Z. Ding, ``Data shuffling in wireless distributed computing via low-rank optimization,"
submitted to \emph{IEEE Trans. Signal Process.}, under first round revision.
\item {\bf{K. Yang}}, Y. Shi, and Z. Ding, ``Generalized
low-rank optimization for topological cooperation in ultra-dense networks,"
submitted to \emph{IEEE Trans. Wireless Commun.}, under second round revision.
\item {{J. Dong}}, {\bf{K. Yang}}, and Y. Shi, ``Ranking from crowdsourced pairwise comparisons via smoothed Riemannian optimization," submitted to {\emph{Signal Process.}}.
\item J. Dong, {\bf{K. Yang}}, and Y. Shi, ``Blind demixing for low-latency communication," in \emph{IEEE
Trans. Wireless Commun.}, vol. 18, no. 2, pp. 897-911, Feb. 2019.
\end{enumerate}

\subsection*{Conference Papers}

\begin{enumerate}
\item \textbf{K. Yang}, T. Jiang, Y. Shi, and Z. Ding, ``Federated learning based on over-the-air computation,'' in \textit{Proc. IEEE Int. Conf. Commun. (ICC)}, Shanghai, China, May 2019.
\item T. Jiang, \textbf{K. Yang}, and Y. Shi, ``Pliable data shuffling for on-device distributed learning,'' in \textit{Proc. IEEE Int. Conf. Acoust. Speech Signal Process. (ICASSP)}, Brighton, UK, May 2019.

\item \textbf{K. Yang}, Y. Shi, and Z. Ding, ``Low-rank optimization for data shuffling in wireless distributed computing,'' in \textit{Proc. IEEE Int. Conf. Acoust. Speech Signal Process. (ICASSP)}, Alberta, Canada,
        Apr. 2018.
        \item J. Dong, \textbf{K. Yang}, and Y. Shi, ``Blind demixing for low-latency communication,'' in \textit{Proc. IEEE Wireless Commun. Networking Conf. (WCNC)}, Barcelona, Spain, Apr. 2018.
        \item \textbf{K. Yang}, Y. Shi, and Z. Ding, ``Generalized matrix completion for low complexity transceiver processing in cache-aided Fog-RAN via the Burer-Monteiro approach,'' in \textit{Proc. IEEE Global Conf. Signal and Inf. Process. (GlobalSIP)}, Montreal, Canada, Nov. 2017.
        \item J. Dong, \textbf{K. Yang}, and Y. Shi, ``Ranking from crowdsourced pairwise comparisons via smoothed matrix manifold optimization,'' in \textit{ICDM Workshops on Data-driven Discovery of Models (D3M)}, New Orleans, Louisiana, USA, Nov. 2017.
        \item \textbf{K. Yang}, Y. Shi, J. Zhang, Z. Ding and K. B. Letaief, ``A low-rank approach for interference management in dense wireless networks,'' in \textit{Proc. IEEE Global Conf. Signal and Inf. Process.(GlobalSIP)}, Washington, DC, Dec. 2016.
        \item \textbf{K. Yang}, Y. Shi, and Z. Ding, ``Low-rank matrix completion for mobile edge caching in Fog-RAN via Riemannian optimization,'' in \textit{Proc. IEEE Global Commun. Conf. (Globecom)}, Washington, DC, Dec. 2016.
        
        
\end{enumerate}


\section*{\colorbox{mygrey}{Technical Backgrounds ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}}
\subsection*{Mathematics}
\begin{minipage}{0.28\linewidth}
 Matrix Analysis
\end{minipage} 
\begin{minipage}{0.4\linewidth}
Stochastic Processes
\end{minipage} 
\begin{minipage}{0.32\linewidth}
 
\end{minipage} 

\subsection*{Optimization} 
\begin{minipage}{0.28\linewidth}
Convex Optimization
\end{minipage}
\begin{minipage}{0.4\linewidth}
Riemannian Optimization
\end{minipage}
\begin{minipage}{0.32\linewidth}

\end{minipage}

\subsection*{Applied Mathematics and Engineering}
\begin{minipage}{0.28\linewidth}
Machine Learning
\end{minipage}
\begin{minipage}{0.20\linewidth}
Deep Learning
\end{minipage}
\begin{minipage}{0.25\linewidth}
Communication Theory
\end{minipage}
\begin{minipage}{0.25\linewidth}
Detection and Estimation
\end{minipage}



\section*{\colorbox{mygrey}{Computer Skills~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}}

Matlab,  Python.


% \bigskip
% % Footer
% \begin{center}
%   \begin{footnotesize}
%     Last updated: \today
%   \end{footnotesize}
% \end{center}

\end{document}

